\textbf{Manual Coding Guidelines\\[0.15cm] for Automation Patents}

### 2015-10-23 manual_coding_guidelines/manual_coding_guidelines.tex
Include Michael Böhm's comments in manual coding guidelines
Typo

\begin{frame}\frametitle{Our sample}
	\begin{itemize}	
	\item We study all U.S. utility patents 1976-2015.
	\item We randomly pick an equal number of patents from all years.
	\item Every patent is reviewed by an additional auditor.
	\item The list of patents is given to the auditor in random (not chronological) order.
	\item We will not share your classifications with anybody, but instead save them with an anonymous coder ID.
\end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Definition}
	\begin{itemize}	
	\item An \textit{automat} is a \textbf{device}$^1$ that carries out a \textbf{process}$^2$ \textbf{independently}$^3$.
		\begin{itemize}	
		\item $^1$: could be a physical machine, computer program, an algorithm, a robot.
		\item $^2$: could be a production process, the act of creation, composing a song, altering something, measuring something, a task
		\item $^3$: without human interference (apart from that needed for supervision, maintenance or at the start) and with a reasonable amount of completeness (so it should not be a minor part of a computer or machine even if that was what we think of as an automat).
		\end{itemize}
		\item What we are not looking for: 
			\begin{itemize}
			\item tools, labor efficiency-enhancing machines
			\item business or production methods and techniques
			\item new chemicals or medical drugs
			\item parts of machines (e.g. a tube) that does not automate or that is not a part of an automat
			\item parts of computers or of sofware that does not directly contribute to automation
			\item highly abstract algorithms (a potential application in automation should be recognizable)
			\end{itemize}			
	\end{itemize}
\end{frame}

>>>>

\begin{frame}\frametitle{Our sample}
	\begin{itemize}	
	\item We study all U.S. patents 1976-2015. 
	\item We only look at *utility patents* which are what we normally think of as patents. Other types of patents we exclude are design patents or plant patents.
	\item We randomly pick an equal number of patents from all years.
	\item Every patent is reviewed by an additional human auditor.
	\item The list of patents is given to the auditor in random (not chronological) order.
	\item We will not share your classifications with anybody, but instead save them with an anonymous coder ID.
\end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Definition}
	\begin{itemize}	
	\item An \textit{automat} is a \textbf{device}$^1$ that carries out a \textbf{process}$^2$ \textbf{independently}$^3$.
		\begin{itemize}	
		\item $^1$: could be a physical machine, computer program, an algorithm, a robot.
		\item $^2$: could be a production process, the act of creation, composing a song, altering something, measuring something, a task
		\item $^3$: without human interference (apart from that needed for supervision, maintenance or at the start) and with a reasonable amount of completeness (so it should not be a minor part of a computer or machine even if that was what we think of as an automat).
		\end{itemize}
		\item What we are not looking for: 
			\begin{itemize}
			\item tools, labor efficiency-enhancing machines
			\item business or production methods and techniques
			\item new chemicals or medical drugs
			\item parts of machines (e.g. a tube) that does not automate or that is not a part of an automat
			\item parts of computers or of software that does not directly contribute to automation
			\item highly abstract algorithms (a potential application in automation should be recognizable)
			\end{itemize}			
	\end{itemize}
\end{frame}
